---
title: "Homework 1"
output: html_notebook
---
setup
```{r}
library(kernlab)
set.seed(42)
```


Q 2.1
Describe a situation or problem from your job, everyday life, current events, etc., for which a classification model would be appropriate. List some (up to 5) predictors that you might use.

As a NFL fan, I often find myself thinking about my team's chances of making to the playoff. I think the classification model would be appropriate in using it to classify NFL teams as playoff contenders or not by midway through the season by looking at a few predictors gathered by midseason. The model will use previous 3 full season's predictors to determine a classifier.

The predictors I'd use to create the classifier would be
 - Touchdowns per game (This will indicate offensive scoring ability of a team)
 - Average wins for opponents in division (How competive is the opponents in the division)
 - Quarterback Rating (How good is the passer of team)
 - Rushing Yards per game (How good are the runners of the team)
 - Wins recorded by mid-season (More likely to be in playoff if they have a winning records by mid season)
 


Q 2.2

```{r}
CCdata <- read.table("credit_card_data.txt", stringsAsFactors = FALSE, header=FALSE)
head(CCdata)
```


